\chapter*{ABSTRACT}
\noindent \textbf{Title:} Development of increased security room access system\newline
\textbf{Author:} Rihards Teteris\newline
\textbf{Advisor:} Researcher, Mg.sc.ing. Roberts Trops\newline
\textbf{Scope of work} 52 pages, 7 figures, 12 bibliographical references, 2 appendices.\newline
\textbf{Keywords:} ROOM, SECURITY, GIT, RUBY, RASPBERRYPI, RFID\newline

The goal of this bachelor's thesis is to develop a secure access system for the work room of  electronics' students.
The main tasks in order to achieve the goal are to create a homepage for administrating the access system of a student work room, which would be using RFID cards for accessing the room, as well as to automate creating the homepage, using RaspberryPi as a server.
The current room access system does not provide sufficient security for the room and the equipment located inside the room. Also, despite the room supposedly being freely accessible to students, in reality the current system does not allow that.

The thesis describes the used version controls, infrastructure as code, testing tools and methods, which provide quick development and implementation without losing quality of the developed product. The homepage created for this thesis is based on web application framework Ruby on Rails. The code written for this thesis is controlled with the Git version control system.

The created system provides much better control over access, as well as easier logging. By implementing this system, the security of the student room would be improved greatly, and the access time issue would also be resolved and the room would be accessible anytime.
